\chapter*{Acknowledgements} %I use an asterisk because I don't want my acknowledgements in the table of contents. I use \chapter to make sure that the acknowledgements go on the correct side of the page when you print out the dissertation.

I'm lucky to have so many people I want to acknowledge that I couldn't possibly put them all here.
Anyone who has offered help with homework, a kind word of encouragement, or shared a beer has my thanks.

Some people deserve special mention here.
To my family, for constant support, while keeping me grounded and sane.
I would never be here without my undergraduate advisor, Stephane Willocq, who spent many more hours helping debug code than I could have ever expected.
Problem sets were only half-terrible due to my brilliant and supportive friends from UMass.

Too many incredible physicists offered many hours of their time throughout my time at Columbia and CERN.
My advisor Emlyn never failed to share his wisdom and a laugh.
If it weren't for Matt, Matt, and Steve, I'd have spent many more hours navigating physics, not to mention the Columbia and ATLAS bureaucracies.
To all my friends from Columbia who suffered through QM and Stat Mech, I'm glad to have finished it with you.

Especially special thanks to Larry Lee and TJ Khoo, both of whom are brilliant, patient, and fun, while also great friends.
Without Chris Rogan and Paul Jackson, the Recursive Jigsaw analysis would never have gotten off the ground, but I would also have had much less fun.
The entire MET group deserves mention, but Silvia Resconi, Claire Lee, and Peter Loch each offered a unique perspective while being supportive and kind.
The support of Laura Jeanty and Karolos Potamianos made the Pixel Lab interesting and fun.

Of friends I didn't work with directly, but who I shared many pistes, beers, and laughs, I'm lucky to say I have too many to list.
Special thanks go to Josh Hardenbrook, Brad Axen, Ryne Carbone, Matt LeBlanc, Tova Holmes, Quentin Buat, Kate Pachal, Karri DePetrillo, Emma Tolley, Jennifer Roloff, and Max Swiatlowski.

To Marisa, thank you for your unwavering support, encouragement, and love.
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
