\documentclass[aps,prd,preprintnumbers,groupedaddress,nofootinbib]{revtex4}

\pdfoutput=1

\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{slashed}
\usepackage{array}
\usepackage{feynmp}
%\usepackage[hypertex]{hyperref}
\usepackage{url}
\usepackage{multirow}


%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\title{Super-Razor and Searches for Sleptons and Charginos at the LHC}

\author{Matthew R.~Buckley$^{1,2}$, Joseph D.~Lykken$^3$, Christopher Rogan$^{4,5}$, and Maria Spiropulu$^4$}
\affiliation{$^1$Center for Particle Astrophysics, Fermi National Accelerator Laboratory, Batavia, IL 60510}
\affiliation{$^2$Department of Physics and Astronomy, Rutgers University, Piscataway, NJ 08954}
\affiliation{$^3$Theoretical Physics Department, Fermi National Accelerator Laboratory, Batavia, IL 60510}
\affiliation{$^4$Lauritsen Laboratory of Physics, California Institute of Technology, Pasadena, CA 91125}
\affiliation{$^5$Department of Physics, Harvard University, Cambridge, MA 02138}

\preprint{FERMILAB-PUB-13-456-A-T, CALT 68-2866}
\date{\today}

\begin{abstract}
Direct searches for electroweak pair production of new particles at the LHC are a difficult proposition, due to the large background and low signal cross sections. We demonstrate how these searches can be improved by a combination of new razor variables and shape analysis of signal and background kinematics. We assume that the pair-produced particles decay to charged leptons and missing energy, either directly or through a $W$ boson. In both cases the final state is a pair of opposite sign leptons plus missing transverse energy. We estimate exclusion reach in terms of sleptons and charginos as realized in minimal supersymmetry. We compare this super-razor approach in detail to analyses based on other kinematic variables, showing how the
super-razor uses more of the relevant kinematic information while achieving higher selection efficiency on
signals, including cases with compressed spectra.
\end{abstract}

\maketitle

\input{sectionI}
\input{sectionII}
\input{sectionIII}
\input{sectionIV}
\input{sectionV}

%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{acknowledgments}
We acknowledge helpful discussions with Paul Jackson, Maurizio Pierini, Chiu-Tien Yu, Javier Duarte and Avi Yagil.   
JL acknowledges the hospitality and support of the Theoretical Physics Group at SLAC.
Fermilab is operated by Fermi Research Alliance, LLC, under contract DE-AC02-07CH11359 with the United States Department of Energy. MS and CR are funded by the United States Department of Energy under Grant DE-FG02-92-ER40701 and acknowledge the support of the Weston Havens Foundation.  
\end{acknowledgments}
%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{apsrev}
\bibliography{superrazor}

\end{document}